\ttlfnt{Comparing the performance of websites and their content distribution networks}

### 2016-08-28 Writeup/paper.tex
Add conclusions

\begin{abstract}
\end{abstract}

@@

\section{Results}\label{sec:results}
\subsection{Home network}
We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular YouTube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular YouTube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929} on a 2 megabits per second (Mbps) ADSL line from Telkom. The Telkom ISP account is uncapped while the rest of the ISP accounts are capped at 1 gigabyte. Table \ref{table:baselineSpeedTests} contains the results from executing a speed test\footnote{Executed at: http://www.speedtest.net} for each ISP. This provides some baseline results for each ISP.

\begin{table}
	\caption{Baseline speed test for each ISP}
	\label{table:baselineSpeedTests}
	\makebox[70mm]{
	\small
	\begin{tabular}{|l|c|c|c|} \hline
		ISP & \small{RTT (ms)} & \small{Downstream (KB/s)} & \small{Upstream (KB/s)} \\ \hline
		Afrihost   & 9   & 215 & 50 \\ \hline
		Axxess     & 10  & 216 & 54 \\ \hline
		Cybersmart & 10  & 214 & 52 \\ \hline
		Telkom     & 12  & 210 & 43 \\ \hline
		WebAfrica  & 10  & 216 & 55 \\ \hline
		\textbf{\textit{Average}}  & \textbf{\textit{10.2}}  & \textbf{\textit{214}} & \textbf{\textit{51}} \\ \hline
	\end{tabular}}
\end{table}

@@

The differences in throughput are not significant and while there are some significant differences in latency, they are not consistent and so are likely due to external factors on the network.
\\\\
\subsubsection{Content server owners}
Although not shown in the tables, it is worth noting the results of the WHOIS lookup for the IPs that served the content. In the case of YouTube, which server provides the content depends on which networks make use of which local caches as well as whether or not the requested content is available in the cache. This is expected as YouTube is a very popular source of content and ISPs setup complex caching systems to reduce bandwidth. For Soundcloud and Twitch.tv however, this is not the case. All Soundcloud content gets delivered from a IP address that is registered to Amazon, suggesting that Soundcloud uses Amazon Web Services for all of its content storage and distribution. The content servers for Twitch.tv are not as consistent. While Afrihost, Telkom and WebAfrica all receive Twitch content from an IP registered to ``MCI Communications Services'' (the same company that is the registered owner of the CDN that hosts the content), Axxess and Cybersmart do not. Axxess routes to a CDN owned by MCI, but the actual content comes from a server owned by ``Akamai International''. Cybersmart does not even receive Twitch content from the same server each time, content arrives from servers that are owned by a variety of other companies.

@@

>>>>

\begin{abstract}
Modern internet infrastructure consists of deep hierarchies of caches and Content Delivery Networks in order to serve the ever-increasing demand for high-bandwidth multimedia content. In this report we present a tool for measuring the impact of Content Delivery Networks on the performance of streaming video and audio content over the internet. We analyse the performance impact of these networks from the point of view both of the home user and large-scale institutions.
\end{abstract}

@@

\section{Results}\label{sec:results}
\subsection{Home network}
We ran our tests on a single home network, gathering measurements for 5 different ISPs (namely Afrihost, Axxess, Cybersmart, Telkom, and WebAfrica) using the same four media URLs\footnote{Unpopular YouTube video: \\ https://www.youtube.com/watch?v=1-xX7hPxMio}\footnote{Popular YouTube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0}\footnote{Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release}\footnote{Twitch.tv video: \\https://www.twitch.tv/dota2ti/v/83400929} on a 2 megabits per second (Mbps) ADSL line from Telkom. The Telkom ISP account is uncapped while the rest of the ISP accounts are capped at 1 gigabyte.

@@

The differences in throughput are not significant and while there are some significant differences in latency, they are not consistent and so are likely due to external factors on the network.

\subsubsection{Content server owners}
Although not shown in the tables, it is worth noting the results of the WHOIS lookup for the IPs that served the content. In the case of YouTube, which server provides the content depends on which networks make use of which local caches as well as whether or not the requested content is available in the cache. This is expected as YouTube is a very popular source of content and ISPs setup complex caching systems to reduce bandwidth. For Soundcloud and Twitch.tv however, this is not the case. All Soundcloud content gets delivered from a IP address that is registered to Amazon, suggesting that Soundcloud uses Amazon Web Services for all of its content storage and distribution. The content servers for Twitch.tv are not as consistent. While Afrihost, Telkom and WebAfrica all receive Twitch content from an IP registered to ``MCI Communications Services'' (the same company that is the registered owner of the CDN that hosts the content), Axxess and Cybersmart do not. Axxess routes to a CDN owned by MCI, but the actual content comes from a server owned by ``Akamai International''. Cybersmart does not even receive Twitch content from the same server each time, content arrives from servers that are owned by a variety of other companies.

@@

\section{Conclusions}
We have developed a tool which can take a list of URLs to a range of multimedia services. It captures a wide range of quantitative metrics such as: RTT, number of hops required to reach the IP, approximate location of IP and organisation hosting IP. Each of the aforementioned metrics are recorded for the resolved IP of the input URL, the IP that the browser is directed to obtain the content from and the IP of the server that actually served up the multimedia content. We also measure the throughput from the multimedia CDN to end-host.

We tested from a number of ISPs on a home network as well as an institutional network. Our results gained insights on the caching behaviour of YouTube with respect to videos with very few views. We found that the majority of unpopular videos are not cached within South Africa. The video has to be obtained from a Google cache in Europe. We found that after viewing the unpopular video it would be cached on both on the ISP's server and Google's South African cache. Subsequent views from the same ISP would come from the ISP cache and views from another ISP would come from Google's South African cache instead of from Europe.

On the institutional network we found that even though, on run 2, the unpopular YouTube video was obtained from the institution's cache, it would always be slower than run 3. It was reasoned that this could be because the cache considers it to be ``hotter'' because of the additional request for it, and serves it at a higher throughput. Another possibility is that while the video is available at the server, the caching process has not fully completed, leading to slower throughput on run 2.
